Comparing \pkg{binsegRcpp} with other implementations of binary segmentation for change-point detection

### 2025-05-08 article.Rnw
wbs

There are several free/open-source implementations of binary
segmentation, most of which use C/C++ code for efficiency
(Table~\ref{tab:packages}).  The \pkg{fpop} package in R contains the
\code{fpop::multiBinSeg} function, which implements the square loss
for multi-dimensional data \citep{Maidstone2017}.  The \pkg{wbs}
package in R contains the \code{wbs::sbs} function, which implements
the square loss for univariate data \citep{Baranowski2019}.  Since it
uses recursive function calls, it does not support the max segments
parameter $K$, and instead always computes the full path of models
(from 1 to $N-1$ change-points).

TODO \code{changepoint::cpt.mean(method="BinSeg")} \citep{Killick2014,Killick2022}.

>>>>

\subsection{Existing implementations of binary segmentation}
There are several free/open-source implementations of binary
segmentation, most of which use C/C++ code for efficiency
(Table~\ref{tab:packages}).
We compared our proposed implementation to these baselines in terms of functionality, correctness, and efficiency.

The \pkg{fpop} package in R contains the \code{fpop::multiBinSeg}
function, which implements the square loss for multi-dimensional data
\citep{Maidstone2017}.

The \pkg{wbs} package in R contains the \code{wbs::sbs} function,
which implements the square loss for univariate data
\citep{Baranowski2019}.  Since it uses recursive function calls, it
does not support the max segments parameter $K$, and instead always
computes the full path of models (from 1 to $N-1$ change-points).

The \code{changepoint::cpt.mean(method="BinSeg")} \citep{Killick2014,Killick2022}.
